---
title: "Heart Exploration"
author: "lizzie"
date: "October 19, 2021"
output:
  pdf_document: default
  word_document: default
---

**Libraries**

```{r}
library(corrplot)
```

**Read .csv**

```{r}
df <- read.csv("Heart_Disease_Prediction.csv")

df$Heart_Disease <- as.numeric(df$Heart_Disease)-1


```


**Look at dataset**

```{r}

summary(df)

```
**Target Variable Counts**
```{r}
table(df$Heart_Disease)
```

**Using Histograms**
```{r}
par(mfrow=c(2,7))

for (i in 1:14){
  hist(df[,i], main=names(df[i]))
}


```
Some of these features are categorical. Some features are normally distributed, and some features are skewed.

**Selecting Features using Pairwise correlation graph**

```{r}
correlations <- cor(df[,1:14])

corrplot(correlations,method = 'circle')

```

Looks like 'Thallium', 'vessels_fluro','Chest', and 'ST_depression' are good indicators.

**Using Histogram to visualize the four features**

```{r}

layout(matrix(1:4, nrow = 1))

features <- c('Thallium', 'vessels_fluro','Chest', 'ST_depression')

df <- df[features]

for (i in 1:4){
  hist(df[,i], main=names(df[i]))
}


```
'Thallium', 'vessels_fluro', and 'Chest' are categorical variables. 'ST_depression' is continous. No need for extreme scaling; all of the variables are within the range of 0 to 10. All histograms are skewed.
